%==================================bibiliography.tex================================
\begin{thebibliography}{99}
	\bibitem{google}Munkhdalai, Tsendsuren, et al. \emph{"Fast Contextual Adaptation with Neural Associative Memory for On-Device Personalized Speech Recognition."} arXiv, 2021, https://doi.org/10.48550/arXiv.2110.02220.
	\bibitem{auto}McClelland, J. L., \& Rumelhart, D. E. (1981). \emph{An interactive activation model of context effects in letter perception: Part 1. An account of basic findings. Psychological Review}, 88(3), 375-407.
	\bibitem{hopfield}Hopfield J. J. (1982). \emph{Neural networks and physical systems with emergent collective computational abilities.} Proceedings of the National Academy of Sciences of the United States of America, 79(8), 2554–2558. https://doi.org/10.1073/pnas.79.8.2554
	\bibitem{spikeprop}Bohté, Sander M. et al. \emph{“SpikeProp: backpropagation for networks of spiking neurons.”} The European Symposium on Artificial Neural Networks (2000).
	\bibitem{leakyintegrate}G. Indiveri, \emph{“A low-power adaptive integrate-and-fire neuron circuit,"} Proceedings of the 2003 International Symposium on Circuits and Systems, 2003. ISCAS '03., 2003, pp. IV-IV, doi: 10.1109/ISCAS.2003.1206342.
	\bibitem{swat}Wade, J. J., McDaid, L. J., Santos, J. A., \& Sayers, H. M. (2010). \emph{SWAT: a spiking neural network training algorithm for classification problems.} IEEE transactions on neural networks, 21(11), 1817–1830. https://doi.org/10.1109/TNN.2010.2074212
	\bibitem{hebbs}Morris R. G. (1999). D.O. \emph{Hebb: The Organization of Behavior,} Wiley: New York; 1949. Brain research bulletin, 50(5-6), 437. https://doi.org/10.1016/s0361-9230(99)00182-3
	\bibitem{stdp}Shouval, H. Z., Wang, S. S., \& Wittenberg, G. M. (2010). \emph{Spike timing dependent plasticity: a consequence of more fundamental learning rules.} Frontiers in computational neuroscience, 4, 19. https://doi.org/10.3389/fncom.2010.00019
	\bibitem{bcm}Bienenstock, E. L., Cooper, L. N., \& Munro, P. W. (1982). \emph{Theory for the development of neuron selectivity: orientation specificity and binocular interaction in visual cortex.} The Journal of neuroscience : the official journal of the Society for Neuroscience, 2(1), 32–48. https://doi.org/10.1523/JNEUROSCI.02-01-00032.1982
	\bibitem{base}He, H., Shang, Y., Yang, X., Di, Y., Lin, J., Zhu, Y., Zheng, W., Zhao, J., Ji, M., Dong, L., Deng, N., Lei, Y., \& Chai, Z. (2019). Constructing an Associative Memory System Using Spiking Neural Network. Frontiers in neuroscience, 13, 650. https://doi.org/10.3389/fnins.2019.00650
	\bibitem{lohi}
	Intel Corporation. (n.d.). LOHI: Low Overhead High Throughput Inference. Retrieved from \url{https://www.intel.com/content/www/us/en/newsroom/news/intel-unveils-neuromorphic-loihi-2-lava-software.html}
	\bibitem{lava}
	Intel Corporation. (n.d.). Lava: Low Overhead Accelerator for Vision Algorithms. Retrieved from \url{https://www.intel.com/content/www/us/en/artificial-intelligence/solutions/inference/lava.html}
	\bibitem{nest}Eppler, J. M., Helias, M., Muller, E., Diesmann, M., \& Gewaltig, M.-O. (2008). NEST (NEural Simulation Tool). Scholarpedia, 3(4), 1430.
	\bibitem{spiketorch}Cao, Y., \& Paine, T. (2020). SpikeTorch: A PyTorch Library for Spiking Neural Networks. arXiv preprint arXiv:2012.13350.

\end{thebibliography}