%==================================introduction.tex=============================
\chapter{Introduction}%

% \addcontentsline{toc}{chapter}{Introduction}%
The ability to store and retrieve associations between different stimuli is a
fundamental component of many cognitive processes, including perception,
learning, and memory. Associative memory is a type of memory system that allows
for the storage and retrieval of information based on the relationships between
different items in memory. It is a key component of a good deal of artificial
intelligence and machine learning systems and has been extensively studied in
both neuroscience and computer science. According to research done by google
for fast contextual adaptation of speech\cite{google} associative memory system
using ANN are efficient in case of contextual adaptation of information.

Spiking neural networks (SNNs) are a type of neural network that can simulate
the dynamics of individual neurons and synapses in the brain. They are
effective for modelling a range of cognitive and sensory processing tasks and
have potential applications in a variety of fields, including computational
neuroscience and machine learning.

Presented in this work is a study on the construction of an associative memory
system using a spiking neural network. This study describes the architecture
and training procedure of the system and evaluates its performance as a
associative memory . It also discusses the implications of the results for the
use of SNNs in implementing associative memory systems and highlights their
potential applications in computational neuroscience and machine learning.

\thispagestyle{plain}