%==================================result.tex=============================
\chapter{Results and Discussion}

\section{Development of the memory layer }
The memory layer of the network did not have any connections between its
neurons during the initialization phase, but new connections began to develop
during the period of structure construction. To memorise various patterns, this
network could develop various connections in the memory layer. The memory could
recall more information with more free space available when the threshold was
set to smaller values since the connection was more sparse.
\section{Recall process}
All of the photographs are utilised to test the recall process as the building
is being built. The identical photographs were then utilised during the
parameter training phase and the trimming phase. There are different reactions
in the memory layer depending on the four different kernels that are used and
illustrated by four images. When a picture is sent into the network, different
components of the picture trigger different firing actions in the network. As
was already mentioned, the firing sequence at the output layer uses a majority
voting technique to decide the outcome of a picture sent into the network. The
outcomes demonstrate that the network was able to recollect the images it had
learned. The network also display some association ability between the newly
learned information and the information that had previously been memorised when
it was given with an unseen but comparable image of digit.